---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Lab5

<!-- badges: start -->
<!-- badges: end -->

Repository for the course Advanced Programming in R at Linköping University. Assignment 5.

We are going to use the Kolada API using JSON, the API has a documentation and follows the REST principle. The documentation can be found here.

A Tutorial how to consume a REST-API in R can be found here.

The packages needed are httr for the HTTP communication and jsonlite for mapping JSON data to data.frames.


## Installation

You can install the development version of Lab5 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aydinardalan/Lab5")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Lab5)
## basic example code
```
