---
title: "Kolada's API"
author: "Aydin Ardalan , Seyed Mehdi Mir Shojaei"
github_user_names: "aydinardalan , seymi176"
liuid: "aydar442 , seymi176"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Lab5

<!-- badges: start -->
[![R-CMD-check](https://github.com/aydinardalan/Lab5/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/aydinardalan/Lab5/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Repository for the course Advanced Programming in R at Linköping University. Assignment 5.

We are going to use the Kolada API using JSON, the API has a documentation and follows the REST principle. The documentation can be found here.

A Tutorial how to consume a REST-API in R can be found here.

The packages needed are httr for the HTTP communication and jsonlite for mapping JSON data to data.frames.


## Installation

You can install the development version of Lab5 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aydinardalan/Lab5")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r , eval = T}
library(Lab5)
Municipality("lund")
head(Municipality_groups("1280"))
kpi("kvinnofridskränkning")
kpi_groups("kostnad")
advancedSearch(kpi_list=list("N07402"),municipality_list=list("1281"),year_list=list(2021))
```
