---
title: "Package For Connecting To Kolada API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package For Connecting To Kolada API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab5)
```


## Package Introduction

This package enables the user to connect to **Kolada API** in order to collect required information from Kolada database that contains key indicators regarding the Swedish municipalities. Data is available through below address:

"http://api.kolada.se/v2/"

Two packages *httr* and *jsonlite* are utilized for fetching data and converting it to a readable format. Several functions are also defined for extracting, organizing and showing the data. Below, are some sample output of the functions.


**Municipality Function**

Takes the municipality name as input and retrieve its *id* and *type*:

```{r}
Municipality("lund")
```

**Municipality_groups Function** 

Shows all available municipalities along with their id and type information.

```{r}
head((Municipality_groups("1281")), 10)
```


**Kpi Function** 

Takes a subject as an argument and shows related *KPI* (Key Performance Indicator).

```{r}
kpi("kvinnofridskränkning")
```

**kpi_groups Function** 

Shows information and available data of a specific kpi group as a list.

```{r}
kpi_groups("kostnad")
```

**advancedSearch Function** 

Takes specific KPI code, municipality code or year and shows related information of the KPI.

```{r}
advancedSearch(kpi_list=list("N07402"),municipality_list=list("1281"),year_list=list(2021))
```



